Cover letter for the original IJRR submission

### 2017-09-29 reviews_tro/reviewer_response.tex

\section{Answers to reviewer 4}

\quot{ I suggest that a few papers related to more general motion and contact planning for multi-legged robots can be added. Particularly, the problem of ``foothold selection'' for 4 or 6-legged robots travelling over uneven terrains is a problem related to the one tackled in the paper. It would be nice to select a few representative works (e.g. from the DARPA Learning Locomotion project or
papers related to the ETHZ StarlETH and ANYmal robots) and explain the differences between those approaches and the problem solved in the paper.}
\as{Thanks for the relevant comment. As observed by the reviewer, our state of the art voluntarily focuses on multi-contact planning related work, but it is relevant
to mention the mentioned papers. We added a paragraph at the end of the state of the art to discuss them. As a matter of fact, we believe these approaches could be considered within
our framework to replace specific parts.}\ndone

\quot{in my opinion a T-RO regular paper should be more self-containing. In several points the authors heavily rely on previous publications, e.g. when presenting the RRT-based planner (Section IV-C). This part should be expanded, describing in more detail what exactly has been changed with respect to the reference paper. }
\as{Thanks for the comment. As it is also suggested by reviewer 1 and the AE, we modified the paper for it to be self contained. The references to previous work now solely indicate
that a detailed method is not a contribution of the present paper. \\ 
In the particular case of Section IV-C, in fact the code of our implementation of the Bi-RRT with respect to the original one is exactly the same, with a single difference: when
traditionally a collision detection predicate is called to validate a configuration, we replace this predicate with a call to the reachability condition. We modified the text to explain this more clearly. As the Bi-RRT is a famous standard algorithm in the literature, we do not think it is necessary to include it in this paper, but will gladly do so if required. }
\qt{$C_{Reach}^0$ can be sampled efficiently thanks to Eq.~5, and can thus be used with any standard motion planner.
Our current implementation uses the Bi-RRT planner [25] provided by the HPP software [26].
Our implementation is exactly the same as the pseudo-code of the original planner (which does not detail the configuration validation method). With respect to a ``classic'' implementation, the only difference is that instead of validating a configuration using collision detection, we validate it with the \textit{reachability condition}.} \done

### 2017-09-29 body/rbprm.tex
updated bi rrt description

\subsection{Computing the guide path in $C_{reach}^0$}
$C_{Reach}^0$ can be sampled efficiently thanks to Eq.~\ref{eq:reachc}, and can thus be used with a standard motion planner.
The only significant change is to replace the collision checking with the \textit{reachability condition}.
Our current implementation of these modifications is based on the Bi-RRT planner \citep{770022} provided by the HPP software~\citep{7759083}. \\

>>>>

\subsection{Computing the guide path in $C_{reach}^0$}
$C_{Reach}^0$ can be sampled efficiently thanks to Eq.~\ref{eq:reachc}, and can thus be used with any standard motion planner.
%~ The only significant change is to replace the collision checking with the \textit{reachability condition}.
Our current implementation uses the Bi-RRT planner \citep{770022} provided by the HPP software~\citep{7759083}.
Our implementation is exactly the same as the pseudo-code of the original planner (which does not detail the configuration validation method). With respect to a ``classic'' implementation, the only difference is that instead of validating a configuration using collision detection, we validate it with the \textit{reachability condition}.\\
